surfing

### 2021-05-11 inst/surfing.Rmd
include wct08 (different format)

@@

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
surfing_table
table(surfing_table$nation)
surfing_table$name
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
```

@@

@@

>>>>

We note in passing that `wct8`, hosted at Lemoore had a different
format from the other venues in the championship, being held in an
artificial wave pool in which every wave was essentially identical (up
to a mirror reflection).  Statistically, there were seven heats of
either 2, 4, 8, or 16 surfers.  We show below how to incorporate the
information present in such observations with the remainder of the
championship using a consistent and intuitive statistical model.

@@

```{r}
surfing_table <- read.table("wct_surfers_table.txt",header=TRUE)
options(width=100)
surfing_table
wildcards <- rownames(surfing_table)[-(1:36)]
wildcards
```

@@

```{r directlogplotofstrenghts}
jjO <- surfing_table$points[1:36]
names(jjO) <- rownames(surfing_table)[1:36]
jjL <- surfing_maxp
jjO <- ordertrans(jjO)
jjL <- ordertrans(jjL)
plot(jjO,jjL,pch=16,log='xy')
fit <- lm(log10(jjL)~log10(jjO))
for(i in seq_along(jjO)){
text(jjO[i],jjL[i],names(jjL)[i],col='gray',pos=4,cex=0.5)
}
abline(fit)
```

@@

```{r dosameptest, cache=TRUE}
samep.test(surfing, c("Ferreira","Medina"))
samep.test(surfing, c("Ferreira","Florence"))
samep.test(surfing, c("Florence","Medina"))
samep.test(surfing, c("Florence","Medina","Ferreira"))
```
